Advantages of mixed quantum gates for information processing

### 2019-03-18 decorrelation/mixed_unitaries.tex
Figure and section 2

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

\noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device. Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.  But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended. If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$. This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.

% \begin{equation}
% 	\tr\left(\mathsf{G}(\rho) \cdot\Sigma_i\right)/2^n = 
% 	 \sum_{j} \mathcal{G}_{ij} \tr\left(\rho \cdot\Sigma_j\right)/2^n
% 	% (\mathcal{G})_{ij} = 
% \end{equation}
% if $\rho=\Sigma_j$, then the only term that survives is

\subsection{Representing CPTP maps}
\noindent CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[]. But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$. A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
\begin{align}
	\vectorize{\mathsf{\tilde G}(\rho)}
		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
\end{align}
We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators.  In this basis,
\begin{equation}
  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
\end{equation}
and
\begin{equation}
	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
\end{equation}
Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} []. Error maps take an especially nice form in this representation:
\begin{equation}\label{eq:process_matrix}
\mathcal{E} =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping. If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. Importantly, if $R$ is diagonal, then the error  is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate. 
% If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$). For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.

\subsection{Defining Mixed Quantum Gates}
\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$). This procedure is operationally indistinguishable from a situation in which we always apply the effective operation, 
\begin{align}
	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i,
\end{align}
which we call a \emph{mixed quantum gate} or MQG. Error metrics can then be computed in terms of the effective error map, 
\begin{equation}
	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
\end{equation}
Two important error metrics are the average gate infidelity, $\epsilon_\mathcal{F}$, and the diamond distance, $\epsilon_\diamond$ \cite{}. These may be represented in terms of the error maps as
\begin{align}
	&\epsilon_\diamond \left(\mathsf{E}\right)
		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
										  - (\error \otimes \mathsf{I}_d)(\rho) \vert\vert_1,\\
	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{\tr{\error} + d}{d^2 + d},
\end{align}
where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.  If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity. 
One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question. the diamond distance is approximately linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.

@@

From this definition, we can use linearity to compute the AGI of an MQC. We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for an MQC than any of the processes being mixed.

@@

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing Useful mixed quantum gates}
\label{sec:mixed_unitary_processes}
Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like a general methodology for producing \textit{useful} mixed quantum channels. In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space. In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps. As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift. In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.

@@

If our primary goal is for our MQC to have increased worst-case performance, then a useful target for constructing MQCs is to minimize the diamond norm. The diamond norm is a non-linear function that in general requires a convex optimizer to compute. However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator. As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQC with error generators $\{G_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j G_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property. Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations. In these situations, one can use convex optimization to solve this problem. Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$. We can then consider the matrix whose columns are the vectorized generators of the error channels for each control, i.e. $G_i$ such that $e^{G_i}=\error_i$. Then we will have $m$, $n\times n$ generators:
\begin{equation}\label{eq:vectorized_generators}
	\bold{G} = \left(\begin{array}{cccc}
		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$. This forms a convex optimization problem, and can be written as:

@@

\subsubsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}
Of course, there are other properties of a channel that one might consider optimizing. Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation. We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:

\begin{equation}\label{eq:vectorized_off_diagonal}
	\bold{R} = \left(\begin{array}{cccc}
		R_{1_{2,1}} & R_{2_{2,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		R_{1_{n-1,n-1}} &  &  R_{m_{n-1,n-1}} \\ 
	\end{array} 	
	\right)
\end{equation}
then again we consider the same minimization problem, where we replace $\bold{G}$ with $\bold{R}$:

@@

% ==============================================================================
% Section: Robustness
% ==============================================================================
\subsection{Additional Constraints}
\subsubsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MQC will degrade. Thus, we would like to design MQCs that are robust to this drift. To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}. Instead of only requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift. If our control generator is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}G_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed quantum gate is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MQC}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MQC as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(G_j(\vec{0}) + \frac{\partial}{\partial\delta_i}G_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} G_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQC will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQC} as:
\begin{equation}\label{eq:MQC-relaxed}
\begin{gathered}
\sum\omega_jD^n_j + \mathcal{O}(\epsilon^2) = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. %A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC.
 Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC. To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
\begin{equation}
{\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
		D^\ell_{1_{1,1}} & D^\ell_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		D^\ell_{1_{n,n}} &  &  D^\ell_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}

@@

\subsubsection{Hamiltonian Norm Regularization}
\label{sec:norm}
While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution. In particular, while this minimization problem is sufficient for supressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error. That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}. To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians. In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:

@@

\subsection{Experimental} % (fold)
\label{sub:experimental}
Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement an MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

\subsection{Representing errors in quantum gates}
\noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device. Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.  But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended. If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$. This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.

% \begin{equation}
% 	\tr\left(\mathsf{G}(\rho) \cdot\Sigma_i\right)/2^n = 
% 	 \sum_{j} \mathcal{G}_{ij} \tr\left(\rho \cdot\Sigma_j\right)/2^n
% 	% (\mathcal{G})_{ij} = 
% \end{equation}
% if $\rho=\Sigma_j$, then the only term that survives is 
 CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[]. But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$. A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
\begin{align}
	\vectorize{\mathsf{\tilde G}(\rho)}
		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
\end{align}
We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).  In this basis,
\begin{equation}
  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
\end{equation}
and
\begin{equation}
	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
\end{equation}
Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} []. Error maps take an especially nice form in this representation:
\begin{equation}\label{eq:process_matrix}
\mathcal{E} =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping []. If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate. \footnote{If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$). For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.}

\subsection{Defining Mixed Quantum Gates}
\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{\tilde G}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$). This procedure is operationally indistinguishable from a situation in which we always apply the effective operation, 
\begin{align}
	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i,
\end{align}
which we call a \emph{mixed quantum gate} or MQG. Error metrics can then be computed in terms of the effective error map, 
\begin{equation}
	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
\end{equation}
Two important error metrics are the average gate infidelity, $\epsilon_\mathcal{F}$, and the diamond distance, $\epsilon_\diamond$ \cite{}. These may be represented in terms of the error maps as
\begin{align}
	&\epsilon_\diamond \left(\mathsf{E}\right)
		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
										  - (\error \otimes \mathsf{I}_d)(\rho) \vert\vert_1,\\
	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{\tr{\mathcal{E}} + d}{d^2 + d},
\end{align}
where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.  If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity [Wallman - Error rates in quantum circuits]. The diamond distance is subaddative [Watroos TQI book] under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the diamond distance of a circuit is less than or equal to the sum of the diamond distances for the component gates.

Because $\epsilon_{\mathcal{F}}$ is linear in the error map, we have:
\begin{equation}
	\epsilon_{\mathcal{F}}\!\left(\mathsf{E}_{\rm eff}\right) = \sum_i w_i \,\epsilon_{\mathcal{F}}(\mathsf{E}_i).
\end{equation}
So there can be little hope of reducing the AGI by combining various implementations. However, the diamond distance is a nonlinear function of error map. The Ky Fan singular value inequality [K. Fan, Maximum properties and inequalities for the eigenvalues of completely continuous operators, Proc. Nat. Acad. Sci. U.S.A. 37 (1951), 760–766] implies that:
\begin{equation}
	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
\end{equation}

One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question. the diamond distance is approximately linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.

@@

From this definition, we can use linearity to compute the AGI of a MQC. We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.

@@

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing Useful mixed quantum gates}
\label{sec:mixed_unitary_processes}
Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels. In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin. In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps. As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivates of the error generators, if we want to consider the sensitivity of the controls to drift. By considering the appropriate collection of vectors and weightings, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.

@@

If our primary goal is for our MQC to have increased worst-case performance, then a useful target for constructing MQCs is to minimize the diamond norm. The diamond norm is a non-linear function that in general requires a convex optimizer to compute. However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator. As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j G_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property. Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce weighting a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations. In these situations, one can use convex optimization to solve this problem. Consider the matrix whose columns are the vectorized error generators at our disposal, i.e. for $m$, $n\times n$ generators:
\begin{equation}\label{eq:vectorized_generators}
	\bold{G} = \left(\begin{array}{cccc}
		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$. This forms a convex optimization problem, and can be written as:

@@

\subsubsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}
Of course, there are other properties of a channel that one might consider optimizing. Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is more amenable to classical simulation. Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$. We can write this error channel as a process matrix, vectorize the $R$ submatrices and consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:

\begin{equation}\label{eq:vectorized_off_diagonal}
	\bold{R} = \left(\begin{array}{cccc}
		R_{1_{1,1}} & R_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		R_{1_{n-1,n-1}} &  &  R_{m_{n-1,n-1}} \\ 
	\end{array} 	
	\right)
\end{equation}
then again we consider the same minimization problem, where we replace $\bold{G}$ with $\bold{R}$:

@@

% ==============================================================================
% Section: Robustness
% ==============================================================================
\subsection{Additional Constraints}
\subsubsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MQC will degrade. Thus, we would like to design MQCs that are robust to this drift. To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}. Instead of only requiring that the error generators average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift. If our control generator is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}G_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed quantum gate is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MQC}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MQC as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(G_j(\vec{0}) + \frac{\partial}{\partial\delta_i}G_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} G_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
\begin{equation}\label{eq:MQC-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.

To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
\begin{equation}
{\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
		D^\ell_{1_{1,1}} & D^\ell_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		D^\ell_{1_{n,n}} &  &  D^\ell_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}

@@

\subsubsection{Hamiltonian Norm Regularization}
\label{sec:norm}
While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution. In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error. That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}. To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians. In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:

@@

\subsection{Experimental} % (fold)
\label{sub:experimental}
Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit. In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}. To implement a MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
